---
title: "P-values from Brodeur et al. 2016 for the tidypvals package"
author: "Jeff Leek"
date: "`r BiocStyle::doc_date()`"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Tutorial for swfdr package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

These p-values come from the paper: ["Star Wars: The Empirics strike back"](https://www.aeaweb.org/articles?id=10.1257/app.20150044) and were downloaded from the author's website [http://marcsangnier.free.fr/research_en.php](http://marcsangnier.free.fr/research_en.php) on 2017-07-23. The file that is downloaded from the site is called
`brodeur_le_sangnier_zylberberg_replication.7z`. The file was unzipped and in the main directory there was a file called `final_stars_supp.dta`. This is where this vignette begins. 

# Set up

## Load packages

```{r packages}
library(foreign)
library(devtools)
library(dplyr)
library(pryr)
```

## Load data

First we load the p-value data using the foreign package

```{r load_data, eval=FALSE}
pdat = read.dta("final_stars_supp.dta")
glimpse(pdat)
```

```{r load_data_hidden, echo=FALSE}
pdat = read.dta("~/data/economics/final_stars_supp.dta")
glimpse(pdat)
```


# Tidy p-values

## Most of the p-values are NA

```{r na_pvals}
table(is.na(pdat$p_value_num))
```

## The t-statistic can be used instead

Most of the t-statistics are observed

```{r na_tstats}
tstat_pvals = 2*(1-pnorm(pdat$t_stat_raw))
table(is.na(tstat_pvals))
```

How do the two p-values compare? 

```{r compare}
quantile((tstat_pvals - pdat$p_value_num),na.rm=T)
plot(tstat_pvals, pdat$p_value_num,pch=19)
```

Mostly they are right on the line, with a few exceptions. Let's look at those in specific:

```{r nomatch}
ind = which(abs(tstat_pvals - pdat$p_value_num) > 0.05)
pdat[ind,] %>% select(journal_id,article_page,first_author)
```

All the p-values that don't match come from just two papers! Let's filter those out of the data set. 

```{r}
pdat = pdat[-ind,]
```


## Select the appropriate columns and clean

```{r select}
brodeur2016 = pdat %>% mutate(pvalue=2*(1-pnorm(t_stat_raw)),journal = journal_id) %>%
  mutate(field="economics", abstract=FALSE) %>%
  mutate(operator = NA, doi = NA, pmid=NA) %>%
  select(pvalue,year,journal,field,
         abstract,operator,doi,pmid) %>%
  filter(!is.na(pvalue))
```


# Save data

```{r save_pvals}
use_data(brodeur2016,overwrite=TRUE)
```


# Session information


```{r session_info}
session_info()
```

