---
title: "Merging and plotting the p-values"
author: "Jeff Leek"
date: "`r BiocStyle::doc_date()`"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Tutorial for swfdr package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Load the packages that are needed

```{r load_data}
library(tidypvals)
library(ggjoy)
library(devtools)
library(dplyr)
library(ggplot2)
```


First we need to eliminate the common DOIs between `chavalarias2016` and `head2015`. To do this we need to take the p-values that are unique to `head2015` using an anti-join, then the p-values unique to `chavalarias2016` using a second anti-join, then the p-values that are common using a semi-join. Then merge those three data sets together. This is to avoid duplicated rows appearing twice in the merged data set. 

```{r allpvals}
aj1 = anti_join(head2015,chavalarias2016)
aj2 = anti_join(chavalarias2016,head2015)
sj1 = semi_join(head2015,chavalarias2016)
allp = rbind(aj1,aj2,sj1)
```

Now we merge in the economics p-values

```{r economics}
allp = rbind(allp,brodeur2016)
```


```{r economics_save_hidden, echo=FALSE}
use_data(allp,overwrite=TRUE)
```

Next we filter out the p-values corresponding to less descriptive fields and order in a way that makes the p-value histograms descending. 

```{r filter_out_fields}
modefunc = function(x){
  d = density(x)
  return(d$x[which.max(d$y)])
}
allp = allp %>% filter(!is.na(field)) %>%
  filter(field != "Multidisciplinary") %>%
  filter(field != "Other") %>%
  group_by(field) %>% 
  mutate(averagep = modefunc(pvalue)) %>%
  ungroup() %>%
  arrange(averagep) %>%
  mutate(field=factor(field,levels=unique(field))) %>%
  filter(pvalue <= 1)
```


Now we can make a [joyplot](https://cran.r-project.org/web/packages/ggjoy/vignettes/introduction.html) of the p-values across different fields. 

```{r}
ggplot(allp,aes(x = pvalue, y = field)) + geom_joy(bandwidth=0.01,fill="lightblue") + theme_joy(grid=FALSE)
```

# Session information


```{r session_info}
session_info()
```


