---
title: "P-values from Chavalarias et al. 2016 for the tidypvals package"
author: "Jeff Leek"
date: "`r BiocStyle::doc_date()`"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Tutorial for swfdr package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

These p-values come from the paper: [Evolution of Reporting P Values in the Biomedical Literature](http://jamanetwork.com/journals/jama/fullarticle/2503172). The csv file for the p-values from medline did not have column names, so to ensure we had the right data we downloaded the MySQL dump from the Dataverse [https://dataverse.harvard.edu/file.xhtml;jsessionid=94274f10cbdbecaaaf6da71ca209?fileId=2801917&version=RELEASED&version=.0](https://dataverse.harvard.edu/file.xhtml;jsessionid=94274f10cbdbecaaaf6da71ca209?fileId=2801917&version=RELEASED&version=.0) on on 2017-07-24. We re-loaded it into a MySQL database and that is where the code starts. 

# Set up

## Load packages

```{r packages}
library(foreign)
library(devtools)
library(dplyr)
library(pryr)
library(readr)
library(stringr)
```

## Load data

First we load the raw data from the database - this code assumes that you are using an Ubuntu instance running on a digital ocean server. If you aren't you may need to change the host name, user name, and password below. 

```{r load_database, eval=FALSE}
my_db = src_mysql(
  dbname = "medline_full_txt_pv", 
  user = "root", 
  password = "*****",
  host = "127.0.0.1")
```




Then we select only the columns that we want

```{r select_db, eval=FALSE}
raw_data = my_db %>% tbl("medline_full_txt_pv") %>%
  select(PMID,sign,value,logvalue,DP,first,format,abs) %>% collect()
```

Then we take on the first appearance of each p-value in the paper

```{r filter_first, eval=FALSE}
raw_data = raw_data %>% filter(first == 1) 
glimpse(raw_data)
```

```{r load_raw_hidden, echo=FALSE}
raw_data = read_csv("~/data/medicine/raw_data.csv")
glimpse(raw_data)
```

We need to add DOIs for all for all of the papers so we can compare them to the Head 2015 data set also included in this package. To do this we need to get data mapping Pubmed IDs to DOIs. We used the bulk data downloaded from NCBI here with that mapping information: [https://www.ncbi.nlm.nih.gov/pmc/pmctopmid/](https://www.ncbi.nlm.nih.gov/pmc/pmctopmid/). We downloaded the file `PMC-ids.csv.gz` on 2017-07-24. 

We load the pubmed to DOI data:

```{r pubmed_to_doi, eval=FALSE}
pmids = read_csv("PMC-ids.csv")
glimpse(pmids)
```


```{r pubmed_to_doi_hidden, echo=FALSE}
pmids = read_csv("~/data/medicine/PMC-ids.csv")
glimpse(pmids)
```


We can now merge by Pubmed ID

```{r merge_ids}
pmids$PMID = as.integer(pmids$PMID)
raw_data = left_join(raw_data,pmids)
glimpse(raw_data)
```


Check to see how many DOIs are not reported, then filter those out

```{r}
mean(is.na(raw_data$DOI))
pdat = raw_data %>% filter(!is.na(DOI))
rm(raw_data)
rm(pmids)
```

Now we load in the journal category data and merge the two together

```{r load_journal_data , eval=FALSE}
journals = read_csv("FILES_FOR_DRYAD/1. TEXT_MINING/raw_data/journal.categories.csv")
glimpse(journals)
```

```{r load_journal_data_hidden, echo=FALSE}
journals = read_csv("~/data/biology/FILES_FOR_DRYAD/1. TEXT_MINING/raw_data/journal.categories.csv")
glimpse(journals)
```


Merge the two data sets together. It appears that the journal abbreviation is the better choice for matching here and that using either of the two is little improvement over just using the abbreviation. 

```{r}
mean(pdat$`Journal Title` %in% journals$Title)
mean(pdat$`Journal Title` %in% journals$Abbreviation)
mean(pdat$`Journal Title` %in% journals$Abbreviation | pdat$`Journal Title` %in% journals$Title)
```


So we merge on Abbreviation

```{r merge}
pdat = left_join(pdat,journals,by=c("Journal Title"="Abbreviation"))
rm(journals)
```


# Tidy p-values


## Format p-values

For each of the formats check if using `as.numeric` is sufficient to re-format the data in double format. 

```{r check_formats}
table(pdat$format)

pdat %>% filter(format=="10exp") %>% head(5) %>% 
  mutate(nump = as.numeric(value)) %>% select(value,nump)

pdat %>% filter(format=="exp") %>% head(5) %>% 
  mutate(nump = as.numeric(value)) %>% select(value,nump)
  
pdat %>% filter(format==".int") %>% head(5) %>% 
     mutate(nump = as.numeric(value)) %>% select(value,nump)
```


It looks good so lets convert the pvalue data to values. 

```{r reformat_pvals}
pdat = pdat %>% mutate(pvalue = as.numeric(value))
```

 
## Select the appropriate columns and clean

Based on comparing to the Head 2015 data set, it appears that abs = 1 means the paper is not in the abstract. 

```{r select}
chavalarias2016 = pdat %>% mutate(journal = `Journal Title`)%>%
  mutate(abstract=(abs==0), doi=DOI) %>%
  mutate(year = DP, pmid=PMID) %>% 
  mutate(field=Category) %>%
  mutate(
    operator = case_when(
     str_detect(sign, "<") | str_detect(sign, "less") ~ "lessthan",
     sign == "="  | sign == "==" ~ "equals" ,
     str_detect(sign, ">") ~ "greaterthan"
  )) %>%
  select(pvalue,year,journal,field,
         abstract,operator,doi,pmid) %>%
  filter(!is.na(pvalue))
```


# Save data

```{r save_pvals}
use_data(chavalarias2016,overwrite=TRUE)
```

# Session information


```{r session_info}
session_info()
```

